Holomorphic field theories and higher algebra

### 2024-09-17 draft.tex
moving small things around

\def\brian#1{{\textcolor{blue!65!red}{BW: {#1}}}}
\def\owen#1{{\textcolor{violet!65!black}{OG: {#1}}}}

@@

@@

This foundational work was motivated in large part by our joint effort to generalize to complex $n$-folds results about chiral conformal theories on Riemann surfaces.
A first fruit of our work \cite{GWcurr} is an examination of higher-dimensional {\em current algebras},
which are factorization algebras that generalize the Kac-Moody vertex algebras that play a crucial role in contemporary representation theory.
We show, for instance, that these current algebras arise as the quantization of symmetries of holomorphic field theories, 
much as the affine Lie algebras are symmetries of CFTs on Riemann surfaces.
In addition, we show that encoded in our factorization algebras are the higher Kac-Moody Lie algebras $\widehat{\g}_{d,\theta}$ of Faonte-Hennion-Kapranov~\cite{FHK}. 
It is striking to find this rigid skeleton of algebra under the meat of our analysis,
as our work is strongly differential-geometric in flavor.
Moreover, as their work provides a direct connection with the derived algebraic geometry of $\RR Bun_G(X)$,
there emerges a beautiful generalization of the fertile interactions between algebraic geometry, representation theory, and physics that have grown around bundles on Riemann surfaces.
(The prospect looms that in higher dimensions,
one might find a correspondence between conformal blocks and nonabelian theta functions.)

A second fruit is a collaboration of Williams with the physicist Ingmar Saberi \cite{SabWil1,SabWil2}.
They have carefully worked out the holomorphic twists of several supersymmetric theories
and given a novel approach, via factorization algebras, to the results of Beem et al \cite{Beem}.
Particularly important for this proposal,
they have shown how important invariants (notably the ``supersymmetric index") of the untwisted, supersymmetric theory can be computed simply in the holomorphic twist.

@@

>>>>

\def\brian#1{{\textcolor{blue!75!red}{BW: {#1}}}}
\def\owen#1{{\textcolor{violet!50!black}{OG: {#1}}}}

@@

\brian{Comparison}

@@

@@

\owen{Old copy that might be recycled into final version}

\brian{Brian's stuff below}
